---
title: "a crosstalk approach"
output: html_notebook
---

Still wondering if I can make this work with crosstalk.  But I cannot, at the moment.  According to [this](https://stackoverflow.com/questions/42974140/crosstalk-filter-polylines-in-leaflet) leaflet shared data only works with markers and does not work with polygons (choropleths).

```{r load packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidycensus)
library(sf)
library(gganimate)
library(crosstalk)
library(leaflet)
```

```{r get ACS data, message=FALSE, warning=FALSE, results='hide'}
nc_2016 <- 
  get_acs(geography = "county",
          variables = "B01003_001",
          state = "NC",
          geometry = TRUE,
          cache_table = TRUE) %>% 
  mutate(year = "2016")

nc_2015 <- 
  get_acs(geography = "county",
          variables = "B01003_001",
          state = "NC",
          year = 2015,
          geometry = TRUE,
          cache_table = TRUE) %>% 
  mutate(year = "2015")

nc_2014 <- 
  get_acs(geography = "county",
          variables = "B01003_001",
          state = "NC",
          year = 2014,
          geometry = TRUE,
          cache_table = TRUE) %>% 
  mutate(year = "2014")

nc_2013 <- 
  get_acs(geography = "county",
          variables = "B01003_001",
          state = "NC",
          year = 2013,
          geometry = TRUE,
          cache_table = TRUE) %>% 
  mutate(year = "2013")
```

## Wrangle Data

Combine the small tables into a big table.  Make a copy of the same with scrambled data via `sample()`.  Additionally, make a scrambled table without sf geometry for use in the bar plot.

```{r wrangle data}
big_table <- rbind(nc_2016, nc_2015, nc_2014, nc_2013) 

nc_2016_r <- nc_2016
nc_2015_r <- nc_2015
nc_2014_r <- nc_2014
nc_2013_r <- nc_2013

nc_2016_r$estimate <- sample(nc_2016_r$estimate)
nc_2015_r$estimate <- sample(nc_2015_r$estimate)
nc_2014_r$estimate <- sample(nc_2014_r$estimate)
nc_2013_r$estimate <- sample(nc_2013_r$estimate)

bg_r <- rbind(nc_2016_r, nc_2015_r, nc_2014_r, nc_2013_r)

bg_r_nogeom <- bg_r
sf::st_geometry(bg_r_nogeom) <- NULL  # remove geometry layer from the SF Tibble

bg_r_small <- bg_r %>% 
  mutate(county = str_extract(NAME, "\\w+")) %>% 
  filter(county == "Orange" | 
         county == "Wake" |
         county == "Durham")

nc_2013_r_small <- nc_2013_r %>% 
  mutate(county = str_extract(NAME, "\\w+")) %>% 
  filter(county == "Orange" | 
         county == "Wake" |
         county == "Durham")

nc_2014_r_small <- nc_2013_r %>% 
  mutate(county = str_extract(NAME, "\\w+")) %>% 
  filter(county == "Orange" | 
         county == "Wake" |
         county == "Durham")


nc_2015_r_small <- nc_2013_r %>% 
  mutate(county = str_extract(NAME, "\\w+")) %>% 
  filter(county == "Orange" | 
         county == "Wake" |
         county == "Durham")


nc_2016_r_small <- nc_2013_r %>% 
  mutate(county = str_extract(NAME, "\\w+")) %>% 
  filter(county == "Orange" | 
         county == "Wake" |
         county == "Durham")

nc_2016_r_small$estimate <-
  sample(nc_2016_r_small$estimate)
nc_2015_r_small$estimate <-
  sample(nc_2015_r_small$estimate)
nc_2014_r_small$estimate <-
  sample(nc_2014_r_small$estimate)
nc_2013_r_small$estimate <-
  sample(nc_2013_r_small$estimate)
```


## Practice 

```{r}
glimpse(bg_r_small)

ggplot() +
  geom_sf(data = bg_r_small %>% filter(year == "2016"),
          aes(fill = estimate, color = estimate))
```

```{r}
pal <- colorNumeric("viridis", NULL)

leaflet(data = bg_r_small %>% filter(year == "2013")) %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(fillColor = ~pal(estimate),
              fillOpacity = 0.8,
              color = "#BDBDC3",
              weight = 1)
```

## Shared Data

https://stackoverflow.com/questions/42974140/crosstalk-filter-polylines-in-leaflet

investigated this but the important part is that this works with a forked version of crosstalk/leaflet that is put in as a pull-request but has not been accepted as of the moment (3/14/2019)

```{r}
bg_r_small_shared <- SharedData$new(bg_r_small)

pal <- colorNumeric("viridis", NULL)


yr_chkb <- filter_checkbox("year_s", "Year", bg_r_small_shared, ~year)

leaf_map <- leaflet(data = bg_r_small_shared %>% filter(year == ~year)) %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(fillColor = ~pal(estimate),
              fillOpacity = 0.8,
              color = "#BDBDC3",
              weight = 1)
```

